### 2017-01-12 doc/manuscript.Rmd
Added some notes to maybe include in discussion

>>>>

NEFA may be a mediating factor in association, but that adjustment will not
attenuate this assoc since TAGFA composition is also dictated by other sources
for DNL (e.g. recent meal, DNL from glucose stores, etc.).

Since no interaction, no loop? Not enough sample, already IR? maybe?

Concentration data is not

Discuss well done paper (very relevant) Kotronen2009a

Prospective cohorts:
    - Chien K, et al. A prediction model for type 2 diabetes risk among Chinese people. Diabetologia. 2009;52(3):443–450.
    - D’Agostino RB Jr, Hamman RF, Karter AJ, Mykkanen L, Wagenknecht LE, Haffner SM. Cardiovascular disease risk factors predict the development of type 2 diabetes: the insulin resistance atherosclerosis study. Diabetes Care. 2004;27(9):2234–2240.
    - Schulze MB, et al. Use of multiple metabolic and genetic markers to improve the prediction of type 2 diabetes: the EPIC-Potsdam Study. Diabetes Care. 2009;32(11):2116–2119.
